---
title: "Model sensitivity analysis [benchmark data]"
author: "Martin R. Vasilev"
date: "May 18, 2016"
output: html_document
---

```{r, echo=FALSE}
#Table 1
load('Summaries/bench/sum1.Rda'); load('Summaries/bench/sum1_3.Rda');load('Summaries/bench/sum1_4.Rda')
load('Summaries/bench/sum1_5.Rda'); load('Summaries/bench/sum1_6.Rda'); load('Summaries/bench/sum1_7.Rda');

#Table 2
load('Summaries/bench/sum2.Rda'); load('Summaries/bench/sum2_3.Rda');load('Summaries/bench/sum2_4.Rda')
load('Summaries/bench/sum2_5.Rda'); load('Summaries/bench/sum2_6.Rda'); load('Summaries/bench/sum2_7.Rda'); 

#Table 3
load('Summaries/bench/sum3.Rda'); load('Summaries/bench/sum3_3.Rda');load('Summaries/bench/sum3_4.Rda')
load('Summaries/bench/sum3_5.Rda'); load('Summaries/bench/sum3_6.Rda'); load('Summaries/bench/sum3_7.Rda'); 

#Table 4
load('Summaries/bench/sum4.Rda'); load('Summaries/bench/sum4_3.Rda');load('Summaries/bench/sum4_4.Rda')
load('Summaries/bench/sum4_5.Rda'); load('Summaries/bench/sum4_6.Rda'); load('Summaries/bench/sum4_7.Rda'); 

#Table 5
load('Summaries/bench/sum5.Rda'); load('Summaries/bench/sum5_3.Rda');load('Summaries/bench/sum5_4.Rda')
load('Summaries/bench/sum5_5.Rda'); load('Summaries/bench/sum5_6.Rda'); load('Summaries/bench/sum5_7.Rda'); 

#Table 6
load('Summaries/bench/sum6.Rda'); load('Summaries/bench/sum6_3.Rda');load('Summaries/bench/sum6_4.Rda')
load('Summaries/bench/sum6_5.Rda'); load('Summaries/bench/sum6_6.Rda'); load('Summaries/bench/sum6_7.Rda');

#Table 7
load('Summaries/bench/sum7.Rda'); load('Summaries/bench/sum7_3.Rda');load('Summaries/bench/sum7_4.Rda')
load('Summaries/bench/sum7_5.Rda'); load('Summaries/bench/sum7_6.Rda'); load('Summaries/bench/sum7_7.Rda'); 

#Table 8
load('Summaries/bench/sum8.Rda'); load('Summaries/bench/sum8_3.Rda');load('Summaries/bench/sum8_4.Rda')
load('Summaries/bench/sum8_5.Rda'); load('Summaries/bench/sum8_6.Rda'); load('Summaries/bench/sum8_7.Rda');

#Table 9
load('Summaries/bench/sum9.Rda'); load('Summaries/bench/sum9_3.Rda');load('Summaries/bench/sum9_4.Rda')
load('Summaries/bench/sum9_5.Rda'); load('Summaries/bench/sum9_6.Rda'); load('Summaries/bench/sum9_7.Rda'); 

#Table 10
load('Summaries/bench/sum10.Rda'); load('Summaries/bench/sum10_3.Rda');load('Summaries/bench/sum10_4.Rda')
load('Summaries/bench/sum10_5.Rda'); load('Summaries/bench/sum10_6.Rda'); load('Summaries/bench/sum10_7.Rda');

#Table 11
load('Summaries/bench/sum11.Rda'); load('Summaries/bench/sum11_3.Rda');load('Summaries/bench/sum11_4.Rda')
load('Summaries/bench/sum11_5.Rda'); load('Summaries/bench/sum11_6.Rda'); load('Summaries/bench/sum11_7.Rda'); 
```

```{r, echo=FALSE}
# numbers (e.g. Mu1) refer to rows in the table

#### Table 1
Mu1= round(sum1$statistics[1,1],2); Mu1_SD= round(sum1$statistics[1,2],2);Mu1CI= round(c(sum1$quantiles[1,1], sum1$quantiles[1,5]) ,2); Mu1CI<- paste(Mu1CI[1], ", ", Mu1CI[2], sep="")
Tau1= round(sum1$statistics[2,1],2); Tau1_SD= round(sum1$statistics[2,2],2);Tau1CI= round(c(sum1$quantiles[2,1], sum1$quantiles[2,5]) ,2); Tau1CI<- paste(Tau1CI[1], ", ", Tau1CI[2], sep="")

Mu2= round(sum1_3$statistics[1,1],2); Mu2_SD= round(sum1_3$statistics[1,2],2);Mu2CI= round(c(sum1_3$quantiles[1,1], sum1_3$quantiles[1,5]) ,2); Mu2CI<- paste(Mu2CI[1], ", ", Mu2CI[2], sep="")
Tau2= round(sum1_3$statistics[2,1],2); Tau2_SD= round(sum1_3$statistics[2,2],2);Tau2CI= round(c(sum1_3$quantiles[2,1], sum1_3$quantiles[2,5]) ,2); Tau2CI<- paste(Tau2CI[1], ", ", Tau2CI[2], sep="")

Mu3= round(sum1_4$statistics[1,1],2); Mu3_SD= round(sum1_4$statistics[1,2],2);Mu3CI= round(c(sum1_4$quantiles[1,1], sum1_4$quantiles[1,5]) ,2); Mu3CI<- paste(Mu3CI[1], ", ", Mu3CI[2], sep="")
Tau3= round(sum1_4$statistics[2,1],2); Tau3_SD= round(sum1_4$statistics[2,2],2);Tau3CI= round(c(sum1_4$quantiles[2,1], sum1_4$quantiles[2,5]) ,2); Tau3CI<- paste(Tau3CI[1], ", ", Tau3CI[2], sep="")

Mu4= round(sum1_5$statistics[1,1],2); Mu4_SD= round(sum1_5$statistics[1,2],2);Mu4CI= round(c(sum1_5$quantiles[1,1], sum1_5$quantiles[1,5]) ,2); Mu4CI<- paste(Mu4CI[1], ", ", Mu4CI[2], sep="")
Tau4= round(sum1_5$statistics[2,1],2); Tau4_SD= round(sum1_5$statistics[2,2],2);Tau4CI= round(c(sum1_5$quantiles[2,1], sum1_5$quantiles[2,5]) ,2); Tau4CI<- paste(Tau4CI[1], ", ", Tau4CI[2], sep="")

Mu5= round(sum1_6$statistics[1,1],2); Mu5_SD= round(sum1_6$statistics[1,2],2);Mu5CI= round(c(sum1_6$quantiles[1,1], sum1_6$quantiles[1,5]) ,2); Mu5CI<- paste(Mu5CI[1], ", ", Mu5CI[2], sep="")
Tau5= round(sum1_6$statistics[2,1],2); Tau5_SD= round(sum1_6$statistics[2,2],2);Tau5CI= round(c(sum1_6$quantiles[2,1], sum1_6$quantiles[2,5]) ,2); Tau5CI<- paste(Tau5CI[1], ", ", Tau5CI[2], sep="")

Mu6= round(sum1_7$statistics[1,1],2); Mu6_SD= round(sum1_7$statistics[1,2],2);Mu6CI= round(c(sum1_7$quantiles[1,1], sum1_7$quantiles[1,5]) ,2); Mu6CI<- paste(Mu6CI[1], ", ", Mu6CI[2], sep="")
Tau6= round(sum1_7$statistics[2,1],2); Tau6_SD= round(sum1_7$statistics[2,2],2);Tau6CI= round(c(sum1_7$quantiles[2,1], sum1_7$quantiles[2,5]) ,2); Tau6CI<- paste(Tau6CI[1], ", ", Tau6CI[2], sep="")


#### Table 2
Mu7= round(sum2$statistics[1,1],2); Mu7_SD= round(sum2$statistics[1,2],2);Mu7CI= round(c(sum2$quantiles[1,1], sum2$quantiles[1,5]) ,2); Mu7CI<- paste(Mu7CI[1], ", ", Mu7CI[2], sep="")
Tau7= round(sum2$statistics[2,1],2); Tau7_SD= round(sum2$statistics[2,2],2);Tau7CI= round(c(sum2$quantiles[2,1], sum2$quantiles[2,5]) ,2); Tau7CI<- paste(Tau7CI[1], ", ", Tau7CI[2], sep="")

Mu8= round(sum2_3$statistics[1,1],2); Mu8_SD= round(sum2_3$statistics[1,2],2);Mu8CI= round(c(sum2_3$quantiles[1,1], sum2_3$quantiles[1,5]) ,2); Mu8CI<- paste(Mu8CI[1], ", ", Mu8CI[2], sep="")
Tau8= round(sum2_3$statistics[2,1],2); Tau8_SD= round(sum2_3$statistics[2,2],2);Tau8CI= round(c(sum2_3$quantiles[2,1], sum2_3$quantiles[2,5]) ,2); Tau8CI<- paste(Tau8CI[1], ", ", Tau8CI[2], sep="")

Mu9= round(sum2_4$statistics[1,1],2); Mu9_SD= round(sum2_4$statistics[1,2],2);Mu9CI= round(c(sum2_4$quantiles[1,1], sum2_4$quantiles[1,5]) ,2); Mu9CI<- paste(Mu9CI[1], ", ", Mu9CI[2], sep="")
Tau9= round(sum2_4$statistics[2,1],2); Tau9_SD= round(sum2_4$statistics[2,2],2);Tau9CI= round(c(sum2_4$quantiles[2,1], sum2_4$quantiles[2,5]) ,2); Tau9CI<- paste(Tau9CI[1], ", ", Tau9CI[2], sep="")

Mu10= round(sum2_5$statistics[1,1],2); Mu10_SD= round(sum2_5$statistics[1,2],2);Mu10CI= round(c(sum2_5$quantiles[1,1], sum2_5$quantiles[1,5]) ,2); Mu10CI<- paste(Mu10CI[1], ", ", Mu10CI[2], sep="")
Tau10= round(sum2_5$statistics[2,1],2); Tau10_SD= round(sum2_5$statistics[2,2],2);Tau10CI= round(c(sum2_5$quantiles[2,1], sum2_5$quantiles[2,5]) ,2); Tau10CI<- paste(Tau10CI[1], ", ", Tau10CI[2], sep="")

Mu11= round(sum2_6$statistics[1,1],2); Mu11_SD= round(sum2_6$statistics[1,2],2);Mu11CI= round(c(sum2_6$quantiles[1,1], sum2_6$quantiles[1,5]) ,2); Mu11CI<- paste(Mu11CI[1], ", ", Mu11CI[2], sep="")
Tau11= round(sum2_6$statistics[2,1],2); Tau11_SD= round(sum2_6$statistics[2,2],2);Tau11CI= round(c(sum2_6$quantiles[2,1], sum2_6$quantiles[2,5]) ,2); Tau11CI<- paste(Tau11CI[1], ", ", Tau11CI[2], sep="")

Mu12= round(sum2_7$statistics[1,1],2); Mu12_SD= round(sum2_7$statistics[1,2],2);Mu12CI= round(c(sum2_7$quantiles[1,1], sum2_7$quantiles[1,5]) ,2); Mu12CI<- paste(Mu12CI[1], ", ", Mu12CI[2], sep="")
Tau12= round(sum2_7$statistics[2,1],2); Tau12_SD= round(sum2_7$statistics[2,2],2);Tau12CI= round(c(sum2_7$quantiles[2,1], sum2_7$quantiles[2,5]) ,2); Tau12CI<- paste(Tau12CI[1], ", ", Tau12CI[2], sep="")


#### Table 3
Mu13= round(sum3$statistics[1,1],2); Mu13_SD= round(sum3$statistics[1,2],2);Mu13CI= round(c(sum3$quantiles[1,1], sum3$quantiles[1,5]) ,2); Mu13CI<- paste(Mu13CI[1], ", ", Mu13CI[2], sep="")
Tau13= round(sum3$statistics[2,1],2); Tau13_SD= round(sum3$statistics[2,2],2);Tau13CI= round(c(sum3$quantiles[2,1], sum3$quantiles[2,5]) ,2); Tau13CI<- paste(Tau13CI[1], ", ", Tau13CI[2], sep="")

Mu14= round(sum3_3$statistics[1,1],2); Mu14_SD= round(sum3_3$statistics[1,2],2);Mu14CI= round(c(sum3_3$quantiles[1,1], sum3_3$quantiles[1,5]) ,2); Mu14CI<- paste(Mu14CI[1], ", ", Mu14CI[2], sep="")
Tau14= round(sum3_3$statistics[2,1],2); Tau14_SD= round(sum3_3$statistics[2,2],2);Tau14CI= round(c(sum3_3$quantiles[2,1], sum3_3$quantiles[2,5]) ,2); Tau14CI<- paste(Tau14CI[1], ", ", Tau14CI[2], sep="")

Mu15= round(sum3_4$statistics[1,1],2); Mu15_SD= round(sum3_4$statistics[1,2],2);Mu15CI= round(c(sum3_4$quantiles[1,1], sum3_4$quantiles[1,5]) ,2); Mu15CI<- paste(Mu15CI[1], ", ", Mu15CI[2], sep="")
Tau15= round(sum3_4$statistics[2,1],2); Tau15_SD= round(sum3_4$statistics[2,2],2);Tau15CI= round(c(sum3_4$quantiles[2,1], sum3_4$quantiles[2,5]) ,2); Tau15CI<- paste(Tau15CI[1], ", ", Tau15CI[2], sep="")

Mu16= round(sum3_5$statistics[1,1],2); Mu16_SD= round(sum3_5$statistics[1,2],2);Mu16CI= round(c(sum3_5$quantiles[1,1], sum3_5$quantiles[1,5]) ,2); Mu16CI<- paste(Mu16CI[1], ", ", Mu16CI[2], sep="")
Tau16= round(sum3_5$statistics[2,1],2); Tau16_SD= round(sum3_5$statistics[2,2],2);Tau16CI= round(c(sum3_5$quantiles[2,1], sum3_5$quantiles[2,5]) ,2); Tau16CI<- paste(Tau16CI[1], ", ", Tau16CI[2], sep="")

Mu17= round(sum3_6$statistics[1,1],2); Mu17_SD= round(sum3_6$statistics[1,2],2);Mu17CI= round(c(sum3_6$quantiles[1,1], sum3_6$quantiles[1,5]) ,2); Mu17CI<- paste(Mu17CI[1], ", ", Mu17CI[2], sep="")
Tau17= round(sum3_6$statistics[2,1],2); Tau17_SD= round(sum3_6$statistics[2,2],2);Tau17CI= round(c(sum3_6$quantiles[2,1], sum3_6$quantiles[2,5]) ,2); Tau17CI<- paste(Tau17CI[1], ", ", Tau17CI[2], sep="")

Mu18= round(sum3_7$statistics[1,1],2); Mu18_SD= round(sum3_7$statistics[1,2],2);Mu18CI= round(c(sum3_7$quantiles[1,1], sum3_7$quantiles[1,5]) ,2); Mu18CI<- paste(Mu18CI[1], ", ", Mu18CI[2], sep="")
Tau18= round(sum3_7$statistics[2,1],2); Tau18_SD= round(sum3_7$statistics[2,2],2);Tau18CI= round(c(sum3_7$quantiles[2,1], sum3_7$quantiles[2,5]) ,2); Tau18CI<- paste(Tau18CI[1], ", ", Tau18CI[2], sep="")


#### Table 4
Mu19= round(sum4$statistics[1,1],2); Mu19_SD= round(sum4$statistics[1,2],2);Mu19CI= round(c(sum4$quantiles[1,1], sum4$quantiles[1,5]) ,2); Mu19CI<- paste(Mu19CI[1], ", ", Mu19CI[2], sep="")
Tau19= round(sum4$statistics[2,1],2); Tau19_SD= round(sum4$statistics[2,2],2);Tau19CI= round(c(sum4$quantiles[2,1], sum4$quantiles[2,5]) ,2); Tau19CI<- paste(Tau19CI[1], ", ", Tau19CI[2], sep="")

Mu20= round(sum4_3$statistics[1,1],2); Mu20_SD= round(sum4_3$statistics[1,2],2);Mu20CI= round(c(sum4_3$quantiles[1,1], sum4_3$quantiles[1,5]) ,2); Mu20CI<- paste(Mu20CI[1], ", ", Mu20CI[2], sep="")
Tau20= round(sum4_3$statistics[2,1],2); Tau20_SD= round(sum4_3$statistics[2,2],2);Tau20CI= round(c(sum4_3$quantiles[2,1], sum4_3$quantiles[2,5]) ,2); Tau20CI<- paste(Tau20CI[1], ", ", Tau20CI[2], sep="")

Mu21= round(sum4_4$statistics[1,1],2); Mu21_SD= round(sum4_4$statistics[1,2],2);Mu21CI= round(c(sum4_4$quantiles[1,1], sum4_4$quantiles[1,5]) ,2); Mu21CI<- paste(Mu21CI[1], ", ", Mu21CI[2], sep="")
Tau21= round(sum4_4$statistics[2,1],2); Tau21_SD= round(sum4_4$statistics[2,2],2);Tau21CI= round(c(sum4_4$quantiles[2,1], sum4_4$quantiles[2,5]) ,2); Tau21CI<- paste(Tau21CI[1], ", ", Tau21CI[2], sep="")

Mu22= round(sum4_5$statistics[1,1],2); Mu22_SD= round(sum4_5$statistics[1,2],2);Mu22CI= round(c(sum4_5$quantiles[1,1], sum4_5$quantiles[1,5]) ,2); Mu22CI<- paste(Mu22CI[1], ", ", Mu22CI[2], sep="")
Tau22= round(sum4_5$statistics[2,1],2); Tau22_SD= round(sum4_5$statistics[2,2],2);Tau22CI= round(c(sum4_5$quantiles[2,1], sum4_5$quantiles[2,5]) ,2); Tau22CI<- paste(Tau22CI[1], ", ", Tau22CI[2], sep="")

Mu23= round(sum4_6$statistics[1,1],2); Mu23_SD= round(sum4_6$statistics[1,2],2);Mu23CI= round(c(sum4_6$quantiles[1,1], sum4_6$quantiles[1,5]) ,2); Mu23CI<- paste(Mu23CI[1], ", ", Mu23CI[2], sep="")
Tau23= round(sum4_6$statistics[2,1],2); Tau23_SD= round(sum4_6$statistics[2,2],2);Tau23CI= round(c(sum4_6$quantiles[2,1], sum4_6$quantiles[2,5]) ,2); Tau23CI<- paste(Tau23CI[1], ", ", Tau23CI[2], sep="")

Mu24= round(sum4_7$statistics[1,1],2); Mu24_SD= round(sum4_7$statistics[1,2],2);Mu24CI= round(c(sum4_7$quantiles[1,1], sum4_7$quantiles[1,5]) ,2); Mu24CI<- paste(Mu24CI[1], ", ", Mu24CI[2], sep="")
Tau24= round(sum4_7$statistics[2,1],2); Tau24_SD= round(sum4_7$statistics[2,2],2);Tau24CI= round(c(sum4_7$quantiles[2,1], sum4_7$quantiles[2,5]) ,2); Tau24CI<- paste(Tau24CI[1], ", ", Tau24CI[2], sep="")


#### Table 5
Mu25= round(sum5$statistics[1,1],2); Mu25_SD= round(sum5$statistics[1,2],2);Mu25CI= round(c(sum5$quantiles[1,1], sum5$quantiles[1,5]) ,2); Mu25CI<- paste(Mu25CI[1], ", ", Mu25CI[2], sep="")
Tau25= round(sum5$statistics[2,1],2); Tau25_SD= round(sum5$statistics[2,2],2);Tau25CI= round(c(sum5$quantiles[2,1], sum5$quantiles[2,5]) ,2); Tau25CI<- paste(Tau25CI[1], ", ", Tau25CI[2], sep="")

Mu26= round(sum5_3$statistics[1,1],2); Mu26_SD= round(sum5_3$statistics[1,2],2);Mu26CI= round(c(sum5_3$quantiles[1,1], sum5_3$quantiles[1,5]) ,2); Mu26CI<- paste(Mu26CI[1], ", ", Mu26CI[2], sep="")
Tau26= round(sum5_3$statistics[2,1],2); Tau26_SD= round(sum5_3$statistics[2,2],2);Tau26CI= round(c(sum5_3$quantiles[2,1], sum5_3$quantiles[2,5]) ,2); Tau26CI<- paste(Tau26CI[1], ", ", Tau26CI[2], sep="")

Mu27= round(sum5_4$statistics[1,1],2); Mu27_SD= round(sum5_4$statistics[1,2],2);Mu27CI= round(c(sum5_4$quantiles[1,1], sum5_4$quantiles[1,5]) ,2); Mu27CI<- paste(Mu27CI[1], ", ", Mu27CI[2], sep="")
Tau27= round(sum5_4$statistics[2,1],2); Tau27_SD= round(sum5_4$statistics[2,2],2);Tau27CI= round(c(sum5_4$quantiles[2,1], sum5_4$quantiles[2,5]) ,2); Tau27CI<- paste(Tau27CI[1], ", ", Tau27CI[2], sep="")

Mu28= round(sum5_5$statistics[1,1],2); Mu28_SD= round(sum5_5$statistics[1,2],2);Mu28CI= round(c(sum5_5$quantiles[1,1], sum5_5$quantiles[1,5]) ,2); Mu28CI<- paste(Mu28CI[1], ", ", Mu28CI[2], sep="")
Tau28= round(sum5_5$statistics[2,1],2); Tau28_SD= round(sum5_5$statistics[2,2],2);Tau28CI= round(c(sum5_5$quantiles[2,1], sum5_5$quantiles[2,5]) ,2); Tau28CI<- paste(Tau28CI[1], ", ", Tau28CI[2], sep="")

Mu29= round(sum5_6$statistics[1,1],2); Mu29_SD= round(sum5_6$statistics[1,2],2);Mu29CI= round(c(sum5_6$quantiles[1,1], sum5_6$quantiles[1,5]) ,2); Mu29CI<- paste(Mu29CI[1], ", ", Mu29CI[2], sep="")
Tau29= round(sum5_6$statistics[2,1],2); Tau29_SD= round(sum5_6$statistics[2,2],2);Tau29CI= round(c(sum5_6$quantiles[2,1], sum5_6$quantiles[2,5]) ,2); Tau29CI<- paste(Tau29CI[1], ", ", Tau29CI[2], sep="")

Mu30= round(sum5_7$statistics[1,1],2); Mu30_SD= round(sum5_7$statistics[1,2],2);Mu30CI= round(c(sum5_7$quantiles[1,1], sum5_7$quantiles[1,5]) ,2); Mu30CI<- paste(Mu30CI[1], ", ", Mu30CI[2], sep="")
Tau30= round(sum5_7$statistics[2,1],2); Tau30_SD= round(sum5_7$statistics[2,2],2);Tau30CI= round(c(sum5_7$quantiles[2,1], sum5_7$quantiles[2,5]) ,2); Tau30CI<- paste(Tau30CI[1], ", ", Tau30CI[2], sep="")

#### Table 6
Mu31= round(sum6$statistics[1,1],2); Mu31_SD= round(sum6$statistics[1,2],2);Mu31CI= round(c(sum6$quantiles[1,1], sum6$quantiles[1,5]) ,2); Mu31CI<- paste(Mu31CI[1], ", ", Mu31CI[2], sep="")
Tau31= round(sum6$statistics[2,1],2); Tau31_SD= round(sum6$statistics[2,2],2);Tau31CI= round(c(sum6$quantiles[2,1], sum6$quantiles[2,5]) ,2); Tau31CI<- paste(Tau31CI[1], ", ", Tau31CI[2], sep="")

Mu32= round(sum6_3$statistics[1,1],2); Mu32_SD= round(sum6_3$statistics[1,2],2);Mu32CI= round(c(sum6_3$quantiles[1,1], sum6_3$quantiles[1,5]) ,2); Mu32CI<- paste(Mu32CI[1], ", ", Mu32CI[2], sep="")
Tau32= round(sum6_3$statistics[2,1],2); Tau32_SD= round(sum6_3$statistics[2,2],2);Tau32CI= round(c(sum6_3$quantiles[2,1], sum6_3$quantiles[2,5]) ,2); Tau32CI<- paste(Tau32CI[1], ", ", Tau32CI[2], sep="")

Mu33= round(sum6_4$statistics[1,1],2); Mu33_SD= round(sum6_4$statistics[1,2],2);Mu33CI= round(c(sum6_4$quantiles[1,1], sum6_4$quantiles[1,5]) ,2); Mu33CI<- paste(Mu33CI[1], ", ", Mu33CI[2], sep="")
Tau33= round(sum6_4$statistics[2,1],2); Tau33_SD= round(sum6_4$statistics[2,2],2);Tau33CI= round(c(sum6_4$quantiles[2,1], sum6_4$quantiles[2,5]) ,2); Tau33CI<- paste(Tau33CI[1], ", ", Tau33CI[2], sep="")

Mu34= round(sum6_5$statistics[1,1],2); Mu34_SD= round(sum6_5$statistics[1,2],2); Mu34CI= round(c(sum6_5$quantiles[1,1], sum6_5$quantiles[1,5]) ,2); Mu34CI<- paste(Mu34CI[1], ", ", Mu34CI[2], sep="")
Tau34= round(sum6_5$statistics[2,1],2); Tau34_SD= round(sum6_5$statistics[2,2],2);Tau34CI= round(c(sum6_5$quantiles[2,1], sum6_5$quantiles[2,5]) ,2); Tau34CI<- paste(Tau34CI[1], ", ", Tau34CI[2], sep="")

Mu35= round(sum6_6$statistics[1,1],2); Mu35_SD= round(sum6_6$statistics[1,2],2);Mu35CI= round(c(sum6_6$quantiles[1,1], sum6_6$quantiles[1,5]) ,2); Mu35CI<- paste(Mu35CI[1], ", ", Mu35CI[2], sep="")
Tau35= round(sum6_6$statistics[2,1],2); Tau35_SD= round(sum6_6$statistics[2,2],2);Tau35CI= round(c(sum6_6$quantiles[2,1], sum6_6$quantiles[2,5]) ,2); Tau35CI<- paste(Tau35CI[1], ", ", Tau35CI[2], sep="")

Mu36= round(sum6_7$statistics[1,1],2); Mu36_SD= round(sum6_7$statistics[1,2],2);Mu36CI= round(c(sum6_7$quantiles[1,1], sum6_7$quantiles[1,5]) ,2); Mu36CI<- paste(Mu36CI[1], ", ", Mu36CI[2], sep="")
Tau36= round(sum6_7$statistics[2,1],2); Tau36_SD= round(sum6_7$statistics[2,2],2);Tau36CI= round(c(sum6_7$quantiles[2,1], sum6_7$quantiles[2,5]) ,2); Tau36CI<- paste(Tau36CI[1], ", ", Tau36CI[2], sep="")

#### Table 7
Mu37= round(sum7$statistics[1,1],2); Mu37_SD= round(sum7$statistics[1,2],2);Mu37CI= round(c(sum7$quantiles[1,1], sum7$quantiles[1,5]) ,2); Mu37CI<- paste(Mu37CI[1], ", ", Mu37CI[2], sep="")
Tau37= round(sum7$statistics[2,1],2); Tau37_SD= round(sum7$statistics[2,2],2);Tau37CI= round(c(sum7$quantiles[2,1], sum7$quantiles[2,5]) ,2); Tau37CI<- paste(Tau37CI[1], ", ", Tau37CI[2], sep="")

Mu38= round(sum7_3$statistics[1,1],2); Mu38_SD= round(sum7_3$statistics[1,2],2);Mu38CI= round(c(sum7_3$quantiles[1,1], sum7_3$quantiles[1,5]) ,2); Mu38CI<- paste(Mu38CI[1], ", ", Mu38CI[2], sep="")
Tau38= round(sum7_3$statistics[2,1],2); Tau38_SD= round(sum7_3$statistics[2,2],2);Tau38CI= round(c(sum7_3$quantiles[2,1], sum7_3$quantiles[2,5]) ,2); Tau38CI<- paste(Tau38CI[1], ", ", Tau38CI[2], sep="")

Mu39= round(sum7_4$statistics[1,1],2); Mu39_SD= round(sum7_4$statistics[1,2],2);Mu39CI= round(c(sum7_4$quantiles[1,1], sum7_4$quantiles[1,5]) ,2); Mu39CI<- paste(Mu39CI[1], ", ", Mu39CI[2], sep="")
Tau39= round(sum7_4$statistics[2,1],2); Tau39_SD= round(sum7_4$statistics[2,2],2);Tau39CI= round(c(sum7_4$quantiles[2,1], sum7_4$quantiles[2,5]) ,2); Tau39CI<- paste(Tau39CI[1], ", ", Tau39CI[2], sep="")

Mu40= round(sum7_5$statistics[1,1],2); Mu40_SD= round(sum7_5$statistics[1,2],2); Mu40CI= round(c(sum7_5$quantiles[1,1], sum7_5$quantiles[1,5]) ,2); Mu40CI<- paste(Mu40CI[1], ", ", Mu40CI[2], sep="")
Tau40= round(sum7_5$statistics[2,1],2); Tau40_SD= round(sum7_5$statistics[2,2],2);Tau40CI= round(c(sum7_5$quantiles[2,1], sum7_5$quantiles[2,5]) ,2); Tau40CI<- paste(Tau40CI[1], ", ", Tau40CI[2], sep="")

Mu41= round(sum7_6$statistics[1,1],2); Mu41_SD= round(sum7_6$statistics[1,2],2);Mu41CI= round(c(sum7_6$quantiles[1,1], sum7_6$quantiles[1,5]) ,2); Mu41CI<- paste(Mu41CI[1], ", ", Mu41CI[2], sep="")
Tau41= round(sum7_6$statistics[2,1],2); Tau41_SD= round(sum7_6$statistics[2,2],2);Tau41CI= round(c(sum7_6$quantiles[2,1], sum7_6$quantiles[2,5]) ,2); Tau41CI<- paste(Tau41CI[1], ", ", Tau41CI[2], sep="")

Mu42= round(sum7_7$statistics[1,1],2); Mu42_SD= round(sum7_7$statistics[1,2],2);Mu42CI= round(c(sum7_7$quantiles[1,1], sum7_7$quantiles[1,5]) ,2); Mu42CI<- paste(Mu42CI[1], ", ", Mu42CI[2], sep="")
Tau42= round(sum7_7$statistics[2,1],2); Tau42_SD= round(sum7_7$statistics[2,2],2);Tau42CI= round(c(sum7_7$quantiles[2,1], sum7_7$quantiles[2,5]) ,2); Tau42CI<- paste(Tau42CI[1], ", ", Tau42CI[2], sep="")

#### Table 8
Mu43= round(sum8$statistics[1,1],2); Mu43_SD= round(sum8$statistics[1,2],2);Mu43CI= round(c(sum8$quantiles[1,1], sum8$quantiles[1,5]) ,2); Mu43CI<- paste(Mu43CI[1], ", ", Mu43CI[2], sep="")
Tau43= round(sum8$statistics[2,1],2); Tau43_SD= round(sum8$statistics[2,2],2);Tau43CI= round(c(sum8$quantiles[2,1], sum8$quantiles[2,5]) ,2); Tau43CI<- paste(Tau43CI[1], ", ", Tau43CI[2], sep="")

Mu44= round(sum8_3$statistics[1,1],2); Mu44_SD= round(sum8_3$statistics[1,2],2);Mu44CI= round(c(sum8_3$quantiles[1,1], sum8_3$quantiles[1,5]) ,2); Mu44CI<- paste(Mu44CI[1], ", ", Mu44CI[2], sep="")
Tau44= round(sum8_3$statistics[2,1],2); Tau44_SD= round(sum8_3$statistics[2,2],2);Tau44CI= round(c(sum8_3$quantiles[2,1], sum8_3$quantiles[2,5]) ,2); Tau44CI<- paste(Tau44CI[1], ", ", Tau44CI[2], sep="")

Mu45= round(sum8_4$statistics[1,1],2); Mu45_SD= round(sum8_4$statistics[1,2],2);Mu45CI= round(c(sum8_4$quantiles[1,1], sum8_4$quantiles[1,5]) ,2); Mu45CI<- paste(Mu45CI[1], ", ", Mu45CI[2], sep="")
Tau45= round(sum8_4$statistics[2,1],2); Tau45_SD= round(sum8_4$statistics[2,2],2);Tau45CI= round(c(sum8_4$quantiles[2,1], sum8_4$quantiles[2,5]) ,2); Tau45CI<- paste(Tau45CI[1], ", ", Tau45CI[2], sep="")

Mu46= round(sum8_5$statistics[1,1],2); Mu46_SD= round(sum8_5$statistics[1,2],2); Mu46CI= round(c(sum8_5$quantiles[1,1], sum8_5$quantiles[1,5]) ,2); Mu46CI<- paste(Mu46CI[1], ", ", Mu46CI[2], sep="")
Tau46= round(sum8_5$statistics[2,1],2); Tau46_SD= round(sum8_5$statistics[2,2],2);Tau46CI= round(c(sum8_5$quantiles[2,1], sum8_5$quantiles[2,5]) ,2); Tau46CI<- paste(Tau46CI[1], ", ", Tau46CI[2], sep="")

Mu47= round(sum8_6$statistics[1,1],2); Mu47_SD= round(sum8_6$statistics[1,2],2);Mu47CI= round(c(sum8_6$quantiles[1,1], sum8_6$quantiles[1,5]) ,2); Mu47CI<- paste(Mu47CI[1], ", ", Mu47CI[2], sep="")
Tau47= round(sum8_6$statistics[2,1],2); Tau47_SD= round(sum8_6$statistics[2,2],2);Tau47CI= round(c(sum8_6$quantiles[2,1], sum8_6$quantiles[2,5]) ,2); Tau47CI<- paste(Tau47CI[1], ", ", Tau47CI[2], sep="")

Mu48= round(sum8_7$statistics[1,1],2); Mu48_SD= round(sum8_7$statistics[1,2],2);Mu48CI= round(c(sum8_7$quantiles[1,1], sum8_7$quantiles[1,5]) ,2); Mu48CI<- paste(Mu48CI[1], ", ", Mu48CI[2], sep="")
Tau48= round(sum8_7$statistics[2,1],2); Tau48_SD= round(sum8_7$statistics[2,2],2);Tau48CI= round(c(sum8_7$quantiles[2,1], sum8_7$quantiles[2,5]) ,2); Tau48CI<- paste(Tau48CI[1], ", ", Tau48CI[2], sep="")

#### Table 9
Mu49= round(sum9$statistics[1,1],2); Mu49_SD= round(sum9$statistics[1,2],2);Mu49CI= round(c(sum9$quantiles[1,1], sum9$quantiles[1,5]) ,2); Mu49CI<- paste(Mu49CI[1], ", ", Mu49CI[2], sep="")
Tau49= round(sum9$statistics[2,1],2); Tau49_SD= round(sum9$statistics[2,2],2);Tau49CI= round(c(sum9$quantiles[2,1], sum9$quantiles[2,5]) ,2); Tau49CI<- paste(Tau49CI[1], ", ", Tau49CI[2], sep="")

Mu50= round(sum9_3$statistics[1,1],2); Mu50_SD= round(sum9_3$statistics[1,2],2);Mu50CI= round(c(sum9_3$quantiles[1,1], sum9_3$quantiles[1,5]) ,2); Mu50CI<- paste(Mu50CI[1], ", ", Mu50CI[2], sep="")
Tau50= round(sum9_3$statistics[2,1],2); Tau50_SD= round(sum9_3$statistics[2,2],2);Tau50CI= round(c(sum9_3$quantiles[2,1], sum9_3$quantiles[2,5]) ,2); Tau50CI<- paste(Tau50CI[1], ", ", Tau50CI[2], sep="")

Mu51= round(sum9_4$statistics[1,1],2); Mu51_SD= round(sum9_4$statistics[1,2],2);Mu51CI= round(c(sum9_4$quantiles[1,1], sum9_4$quantiles[1,5]) ,2); Mu51CI<- paste(Mu51CI[1], ", ", Mu51CI[2], sep="")
Tau51= round(sum9_4$statistics[2,1],2); Tau51_SD= round(sum9_4$statistics[2,2],2);Tau51CI= round(c(sum9_4$quantiles[2,1], sum9_4$quantiles[2,5]) ,2); Tau51CI<- paste(Tau51CI[1], ", ", Tau51CI[2], sep="")

Mu52= round(sum9_5$statistics[1,1],2); Mu52_SD= round(sum9_5$statistics[1,2],2); Mu52CI= round(c(sum9_5$quantiles[1,1], sum9_5$quantiles[1,5]) ,2); Mu52CI<- paste(Mu52CI[1], ", ", Mu52CI[2], sep="")
Tau52= round(sum9_5$statistics[2,1],2); Tau52_SD= round(sum9_5$statistics[2,2],2);Tau52CI= round(c(sum9_5$quantiles[2,1], sum9_5$quantiles[2,5]) ,2); Tau52CI<- paste(Tau52CI[1], ", ", Tau52CI[2], sep="")

Mu53= round(sum9_6$statistics[1,1],2); Mu53_SD= round(sum9_6$statistics[1,2],2);Mu53CI= round(c(sum9_6$quantiles[1,1], sum9_6$quantiles[1,5]) ,2); Mu53CI<- paste(Mu53CI[1], ", ", Mu53CI[2], sep="")
Tau53= round(sum9_6$statistics[2,1],2); Tau53_SD= round(sum9_6$statistics[2,2],2);Tau53CI= round(c(sum9_6$quantiles[2,1], sum9_6$quantiles[2,5]) ,2); Tau53CI<- paste(Tau53CI[1], ", ", Tau53CI[2], sep="")

Mu54= round(sum9_7$statistics[1,1],2); Mu54_SD= round(sum9_7$statistics[1,2],2);Mu54CI= round(c(sum9_7$quantiles[1,1], sum9_7$quantiles[1,5]) ,2); Mu54CI<- paste(Mu54CI[1], ", ", Mu54CI[2], sep="")
Tau54= round(sum9_7$statistics[2,1],2); Tau54_SD= round(sum9_7$statistics[2,2],2);Tau54CI= round(c(sum9_7$quantiles[2,1], sum9_7$quantiles[2,5]) ,2); Tau54CI<- paste(Tau54CI[1], ", ", Tau54CI[2], sep="")

#### Table 10
Mu55= round(sum10$statistics[1,1],2); Mu55_SD= round(sum10$statistics[1,2],2);Mu55CI= round(c(sum10$quantiles[1,1], sum10$quantiles[1,5]) ,2); Mu55CI<- paste(Mu55CI[1], ", ", Mu55CI[2], sep="")
Tau55= round(sum10$statistics[2,1],2); Tau55_SD= round(sum10$statistics[2,2],2);Tau55CI= round(c(sum10$quantiles[2,1], sum10$quantiles[2,5]) ,2); Tau55CI<- paste(Tau55CI[1], ", ", Tau55CI[2], sep="")

Mu56= round(sum10_3$statistics[1,1],2); Mu56_SD= round(sum10_3$statistics[1,2],2);Mu56CI= round(c(sum10_3$quantiles[1,1], sum10_3$quantiles[1,5]) ,2); Mu56CI<- paste(Mu56CI[1], ", ", Mu56CI[2], sep="")
Tau56= round(sum10_3$statistics[2,1],2); Tau56_SD= round(sum10_3$statistics[2,2],2);Tau56CI= round(c(sum10_3$quantiles[2,1], sum10_3$quantiles[2,5]) ,2); Tau56CI<- paste(Tau56CI[1], ", ", Tau56CI[2], sep="")

Mu57= round(sum10_4$statistics[1,1],2); Mu57_SD= round(sum10_4$statistics[1,2],2);Mu57CI= round(c(sum10_4$quantiles[1,1], sum10_4$quantiles[1,5]) ,2); Mu57CI<- paste(Mu57CI[1], ", ", Mu57CI[2], sep="")
Tau57= round(sum10_4$statistics[2,1],2); Tau57_SD= round(sum10_4$statistics[2,2],2);Tau57CI= round(c(sum10_4$quantiles[2,1], sum10_4$quantiles[2,5]) ,2); Tau57CI<- paste(Tau57CI[1], ", ", Tau57CI[2], sep="")

Mu58= round(sum10_5$statistics[1,1],2); Mu58_SD= round(sum10_5$statistics[1,2],2); Mu58CI= round(c(sum10_5$quantiles[1,1], sum10_5$quantiles[1,5]) ,2); Mu58CI<- paste(Mu58CI[1], ", ", Mu58CI[2], sep="")
Tau58= round(sum10_5$statistics[2,1],2); Tau58_SD= round(sum10_5$statistics[2,2],2);Tau58CI= round(c(sum10_5$quantiles[2,1], sum10_5$quantiles[2,5]) ,2); Tau58CI<- paste(Tau58CI[1], ", ", Tau58CI[2], sep="")

Mu59= round(sum10_6$statistics[1,1],2); Mu59_SD= round(sum10_6$statistics[1,2],2);Mu59CI= round(c(sum10_6$quantiles[1,1], sum10_6$quantiles[1,5]) ,2); Mu59CI<- paste(Mu59CI[1], ", ", Mu59CI[2], sep="")
Tau59= round(sum10_6$statistics[2,1],2); Tau59_SD= round(sum10_6$statistics[2,2],2);Tau59CI= round(c(sum10_6$quantiles[2,1], sum10_6$quantiles[2,5]) ,2); Tau59CI<- paste(Tau59CI[1], ", ", Tau59CI[2], sep="")

Mu60= round(sum10_7$statistics[1,1],2); Mu60_SD= round(sum10_7$statistics[1,2],2);Mu60CI= round(c(sum10_7$quantiles[1,1], sum10_7$quantiles[1,5]) ,2); Mu60CI<- paste(Mu60CI[1], ", ", Mu60CI[2], sep="")
Tau60= round(sum10_7$statistics[2,1],2); Tau60_SD= round(sum10_7$statistics[2,2],2);Tau60CI= round(c(sum10_7$quantiles[2,1], sum10_7$quantiles[2,5]) ,2); Tau60CI<- paste(Tau60CI[1], ", ", Tau60CI[2], sep="")

#### Table 11
Mu61= round(sum11$statistics[1,1],2); Mu61_SD= round(sum11$statistics[1,2],2);Mu61CI= round(c(sum11$quantiles[1,1], sum11$quantiles[1,5]) ,2); Mu61CI<- paste(Mu61CI[1], ", ", Mu61CI[2], sep="")
Tau61= round(sum11$statistics[2,1],2); Tau61_SD= round(sum11$statistics[2,2],2);Tau61CI= round(c(sum11$quantiles[2,1], sum11$quantiles[2,5]) ,2); Tau61CI<- paste(Tau61CI[1], ", ", Tau61CI[2], sep="")

Mu62= round(sum11_3$statistics[1,1],2); Mu62_SD= round(sum11_3$statistics[1,2],2);Mu62CI= round(c(sum11_3$quantiles[1,1], sum11_3$quantiles[1,5]) ,2); Mu62CI<- paste(Mu62CI[1], ", ", Mu62CI[2], sep="")
Tau62= round(sum11_3$statistics[2,1],2); Tau62_SD= round(sum11_3$statistics[2,2],2);Tau62CI= round(c(sum11_3$quantiles[2,1], sum11_3$quantiles[2,5]) ,2); Tau62CI<- paste(Tau62CI[1], ", ", Tau62CI[2], sep="")

Mu63= round(sum11_4$statistics[1,1],2); Mu63_SD= round(sum11_4$statistics[1,2],2);Mu63CI= round(c(sum11_4$quantiles[1,1], sum11_4$quantiles[1,5]) ,2); Mu63CI<- paste(Mu63CI[1], ", ", Mu63CI[2], sep="")
Tau63= round(sum11_4$statistics[2,1],2); Tau63_SD= round(sum11_4$statistics[2,2],2);Tau63CI= round(c(sum11_4$quantiles[2,1], sum11_4$quantiles[2,5]) ,2); Tau63CI<- paste(Tau63CI[1], ", ", Tau63CI[2], sep="")

Mu64= round(sum11_5$statistics[1,1],2); Mu64_SD= round(sum11_5$statistics[1,2],2); Mu64CI= round(c(sum11_5$quantiles[1,1], sum11_5$quantiles[1,5]) ,2); Mu64CI<- paste(Mu64CI[1], ", ", Mu64CI[2], sep="")
Tau64= round(sum11_5$statistics[2,1],2); Tau64_SD= round(sum11_5$statistics[2,2],2);Tau64CI= round(c(sum11_5$quantiles[2,1], sum11_5$quantiles[2,5]) ,2); Tau64CI<- paste(Tau64CI[1], ", ", Tau64CI[2], sep="")

Mu65= round(sum11_6$statistics[1,1],2); Mu65_SD= round(sum11_6$statistics[1,2],2);Mu65CI= round(c(sum11_6$quantiles[1,1], sum11_6$quantiles[1,5]) ,2); Mu65CI<- paste(Mu65CI[1], ", ", Mu65CI[2], sep="")
Tau65= round(sum11_6$statistics[2,1],2); Tau65_SD= round(sum11_6$statistics[2,2],2);Tau65CI= round(c(sum11_6$quantiles[2,1], sum11_6$quantiles[2,5]) ,2); Tau65CI<- paste(Tau65CI[1], ", ", Tau65CI[2], sep="")

Mu66= round(sum11_7$statistics[1,1],2); Mu66_SD= round(sum11_7$statistics[1,2],2);Mu66CI= round(c(sum11_7$quantiles[1,1], sum11_7$quantiles[1,5]) ,2); Mu66CI<- paste(Mu66CI[1], ", ", Mu66CI[2], sep="")
Tau66= round(sum11_7$statistics[2,1],2); Tau66_SD= round(sum11_7$statistics[2,2],2);Tau66CI= round(c(sum11_7$quantiles[2,1], sum11_7$quantiles[2,5]) ,2); Tau66CI<- paste(Tau66CI[1], ", ", Tau66CI[2], sep="")

```

Baseline fixation durations for all studies [FFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu1` (`r Mu1_SD`) [`r Mu1CI`] |`r Tau1` (`r Tau1_SD`) [`r Tau1CI`]|
Normal(0, $100^2$) |Uniform(0, 800)     |`r Mu2` (`r Mu2_SD`) [`r Mu2CI`] |`r Tau2` (`r Tau2_SD`) [`r Tau2CI`]|
Uniform(0, 800)|Gamma(0.001, 0.001)|`r Mu3` (`r Mu3_SD`) [`r Mu3CI`] |`r Tau3` (`r Tau3_SD`) [`r Tau3CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu4` (`r Mu4_SD`) [`r Mu4CI`] |`r Tau4` (`r Tau4_SD`) [`r Tau4CI`]|
Uniform(0, 800)|Normal(0, $100^2$) I(0,)|`r Mu5` (`r Mu5_SD`) [`r Mu5CI`] |`r Tau5` (`r Tau5_SD`) [`r Tau5CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu6` (`r Mu6_SD`) [`r Mu6CI`] |`r Tau6` (`r Tau6_SD`) [`r Tau6CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for all studies [SFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu7` (`r Mu7_SD`) [`r Mu7CI`] |`r Tau7` (`r Tau7_SD`) [`r Tau7CI`]|
Normal(0, $100^2$) |Uniform(0, 800)     |`r Mu8` (`r Mu8_SD`) [`r Mu8CI`] |`r Tau8` (`r Tau8_SD`) [`r Tau8CI`]|
Uniform(0, 800)    |Gamma(0.001, 0.001)|`r Mu9` (`r Mu9_SD`) [`r Mu9CI`] |`r Tau9` (`r Tau9_SD`) [`r Tau9CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu10` (`r Mu10_SD`) [`r Mu10CI`] |`r Tau10` (`r Tau10_SD`) [`r Tau10CI`]|
Uniform(0, 800)    |Normal(0, $100^2$) I(0,)|`r Mu11` (`r Mu11_SD`) [`r Mu11CI`] |`r Tau11` (`r Tau11_SD`) [`r Tau11CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu12` (`r Mu12_SD`) [`r Mu12CI`] |`r Tau12` (`r Tau12_SD`) [`r Tau12CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for all studies [GD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 1000)**|**Uniform(0, 1000)**|`r Mu13` (`r Mu13_SD`) [`r Mu13CI`] |`r Tau13` (`r Tau13_SD`) [`r Tau13CI`]|
Normal(0, $100^2$) |Uniform(0, 1000)     |`r Mu14` (`r Mu14_SD`) [`r Mu14CI`] |`r Tau14` (`r Tau14_SD`) [`r Tau14CI`]|
Uniform(0, 1000)   |Gamma(0.001, 0.001)|`r Mu15` (`r Mu15_SD`) [`r Mu15CI`] |`r Tau15` (`r Tau15_SD`) [`r Tau15CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu16` (`r Mu16_SD`) [`r Mu16CI`] |`r Tau16` (`r Tau16_SD`) [`r Tau16CI`]|
Uniform(0, 1000)   |Normal(0, $100^2$) I(0,)|`r Mu17` (`r Mu17_SD`) [`r Mu17CI`] |`r Tau17` (`r Tau17_SD`) [`r Tau17CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu18` (`r Mu18_SD`) [`r Mu18CI`] |`r Tau18` (`r Tau18_SD`) [`r Tau18CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for all studies [TVT]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 1000)**|**Uniform(0, 1000)**|`r Mu19` (`r Mu19_SD`) [`r Mu19CI`] |`r Tau19` (`r Tau19_SD`) [`r Tau19CI`]|
Normal(0, $100^2$) |Uniform(0, 1000)     |`r Mu20` (`r Mu20_SD`) [`r Mu20CI`] |`r Tau20` (`r Tau20_SD`) [`r Tau20CI`]|
Uniform(0, 1000)   |Gamma(0.001, 0.001)|`r Mu21` (`r Mu21_SD`) [`r Mu21CI`] |`r Tau21` (`r Tau21_SD`) [`r Tau21CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu22` (`r Mu22_SD`) [`r Mu22CI`] |`r Tau22` (`r Tau22_SD`) [`r Tau22CI`]|
Uniform(0, 1000)   |Normal(0, $100^2$) I(0,)|`r Mu23` (`r Mu23_SD`) [`r Mu23CI`] |`r Tau23` (`r Tau23_SD`) [`r Tau23CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu24` (`r Mu24_SD`) [`r Mu24CI`] |`r Tau24` (`r Tau24_SD`) [`r Tau24CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for alphabetical studies [FFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu25` (`r Mu25_SD`) [`r Mu25CI`] |`r Tau25` (`r Tau25_SD`) [`r Tau25CI`]|
Normal(0, $100^2$) |Uniform(0, 800)     |`r Mu26` (`r Mu26_SD`) [`r Mu26CI`] |`r Tau26` (`r Tau26_SD`) [`r Tau26CI`]|
Uniform(0, 800)|Gamma(0.001, 0.001)|`r Mu27` (`r Mu27_SD`) [`r Mu27CI`] |`r Tau27` (`r Tau27_SD`) [`r Tau27CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu28` (`r Mu28_SD`) [`r Mu28CI`] |`r Tau28` (`r Tau28_SD`) [`r Tau28CI`]|
Uniform(0, 800)|Normal(0, $100^2$) I(0,)|`r Mu29` (`r Mu29_SD`) [`r Mu29CI`] |`r Tau29` (`r Tau29_SD`) [`r Tau29CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu30` (`r Mu30_SD`) [`r Mu30CI`] |`r Tau30` (`r Tau30_SD`) [`r Tau30CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for alphabetical studies [SFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu31` (`r Mu31_SD`) [`r Mu31CI`] |`r Tau31` (`r Tau31_SD`) [`r Tau31CI`]|
Normal(0, $100^2$) |Uniform(0, 800)     |`r Mu32` (`r Mu32_SD`) [`r Mu32CI`] |`r Tau32` (`r Tau32_SD`) [`r Tau32CI`]|
Uniform(0, 800)    |Gamma(0.001, 0.001)|`r Mu33` (`r Mu33_SD`) [`r Mu33CI`] |`r Tau33` (`r Tau33_SD`) [`r Tau33CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu34` (`r Mu34_SD`) [`r Mu34CI`] |`r Tau34` (`r Tau34_SD`) [`r Tau34CI`]|
Uniform(0, 800)    |Normal(0, $100^2$) I(0,)|`r Mu35` (`r Mu35_SD`) [`r Mu35CI`] |`r Tau35` (`r Tau35_SD`) [`r Tau35CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu36` (`r Mu36_SD`) [`r Mu36CI`] |`r Tau36` (`r Tau36_SD`) [`r Tau36CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for alphabetical studies [GD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 1000)**|**Uniform(0, 1000)**|`r Mu37` (`r Mu37_SD`) [`r Mu37CI`] |`r Tau37` (`r Tau37_SD`) [`r Tau37CI`]|
Normal(0, $100^2$) |Uniform(0, 1000)     |`r Mu38` (`r Mu38_SD`) [`r Mu38CI`] |`r Tau38` (`r Tau38_SD`) [`r Tau38CI`]|
Uniform(0, 1000)   |Gamma(0.001, 0.001)|`r Mu39` (`r Mu39_SD`) [`r Mu39CI`] |`r Tau39` (`r Tau39_SD`) [`r Tau39CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu40` (`r Mu40_SD`) [`r Mu40CI`] |`r Tau40` (`r Tau40_SD`) [`r Tau40CI`]|
Uniform(0, 1000)   |Normal(0, $100^2$) I(0,)|`r Mu41` (`r Mu41_SD`) [`r Mu41CI`] |`r Tau41` (`r Tau41_SD`) [`r Tau41CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu42` (`r Mu42_SD`) [`r Mu42CI`] |`r Tau42` (`r Tau42_SD`) [`r Tau42CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for all studies [TVT]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 1000)**|**Uniform(0, 1000)**|`r Mu43` (`r Mu43_SD`) [`r Mu43CI`] |`r Tau43` (`r Tau43_SD`) [`r Tau43CI`]|
Normal(0, $100^2$) |Uniform(0, 1000)     |`r Mu44` (`r Mu44_SD`) [`r Mu44CI`] |`r Tau44` (`r Tau44_SD`) [`r Tau44CI`]|
Uniform(0, 1000)   |Gamma(0.001, 0.001)|`r Mu45` (`r Mu45_SD`) [`r Mu45CI`] |`r Tau45` (`r Tau45_SD`) [`r Tau45CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu46` (`r Mu46_SD`) [`r Mu46CI`] |`r Tau46` (`r Tau46_SD`) [`r Tau46CI`]|
Uniform(0, 1000)   |Normal(0, $100^2$) I(0,)|`r Mu47` (`r Mu47_SD`) [`r Mu47CI`] |`r Tau47` (`r Tau47_SD`) [`r Tau47CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu48` (`r Mu48_SD`) [`r Mu48CI`] |`r Tau48` (`r Tau48_SD`) [`r Tau48CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for Chinese studies [FFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu49` (`r Mu49_SD`) [`r Mu49CI`] |`r Tau49` (`r Tau49_SD`) [`r Tau49CI`]|
Normal(0, $100^2$) |Uniform(0, 800)  |`r Mu50` (`r Mu50_SD`) [`r Mu50CI`] |`r Tau50` (`r Tau50_SD`) [`r Tau50CI`]|
Uniform(0, 800)|Gamma(0.001, 0.001)  |`r Mu51` (`r Mu51_SD`) [`r Mu51CI`] |`r Tau51` (`r Tau51_SD`) [`r Tau51CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu52` (`r Mu52_SD`) [`r Mu52CI`] |`r Tau52` (`r Tau52_SD`) [`r Tau52CI`]|
Uniform(0, 800)|Normal(0, $100^2$) I(0,)|`r Mu53` (`r Mu53_SD`) [`r Mu53CI`] |`r Tau53` (`r Tau53_SD`) [`r Tau53CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu54` (`r Mu54_SD`) [`r Mu54CI`] |`r Tau54` (`r Tau54_SD`) [`r Tau54CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for Chinese studies [SFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 800)**|**Uniform(0, 800)**|`r Mu55` (`r Mu55_SD`) [`r Mu55CI`] |`r Tau55` (`r Tau55_SD`) [`r Tau55CI`]|
Normal(0, $100^2$) |Uniform(0, 800)     |`r Mu56` (`r Mu56_SD`) [`r Mu56CI`] |`r Tau56` (`r Tau56_SD`) [`r Tau56CI`]|
Uniform(0, 800)    |Gamma(0.001, 0.001)|`r Mu57` (`r Mu57_SD`) [`r Mu57CI`] |`r Tau57` (`r Tau57_SD`) [`r Tau57CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu58` (`r Mu58_SD`) [`r Mu58CI`] |`r Tau58` (`r Tau58_SD`) [`r Tau58CI`]|
Uniform(0, 800)    |Normal(0, $100^2$) I(0,)|`r Mu59` (`r Mu59_SD`) [`r Mu59CI`] |`r Tau59` (`r Tau59_SD`) [`r Tau59CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu60` (`r Mu60_SD`) [`r Mu60CI`] |`r Tau60` (`r Tau60_SD`) [`r Tau60CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 


Baseline fixation durations for Chinese studies [GD]
-----------------------------------------------------------------------------------------------------------
Prior on $\mu$   | Prior on $\tau$   | Posterior $\mu$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(0, 1000)**|**Uniform(0, 1000)**|`r Mu61` (`r Mu61_SD`) [`r Mu61CI`] |`r Tau61` (`r Tau61_SD`) [`r Tau61CI`]|
Normal(0, $100^2$) |Uniform(0, 1000)     |`r Mu62` (`r Mu62_SD`) [`r Mu62CI`] |`r Tau62` (`r Tau62_SD`) [`r Tau62CI`]|
Uniform(0, 1000)   |Gamma(0.001, 0.001)|`r Mu63` (`r Mu63_SD`) [`r Mu63CI`] |`r Tau63` (`r Tau63_SD`) [`r Tau63CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu64` (`r Mu64_SD`) [`r Mu64CI`] |`r Tau64` (`r Tau64_SD`) [`r Tau64CI`]|
Uniform(0, 1000)   |Normal(0, $100^2$) I(0,)|`r Mu65` (`r Mu65_SD`) [`r Mu65CI`] |`r Tau65` (`r Tau65_SD`) [`r Tau65CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu66` (`r Mu66_SD`) [`r Mu66CI`] |`r Tau66` (`r Tau66_SD`) [`r Tau66CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 
