---
title: "Model sensitivity analysis [meta-regression]"
author: "Martin R. Vasilev"
date: "May 18, 2016"
output: html_document
---

```{r, echo=FALSE}
# uniform prior on beta:
load('Summaries/N1/sumR1.Rda'); load('Summaries/N1/sumR2.Rda'); load('Summaries/N1/sumR3.Rda');
load('Summaries/N1/sumR4.Rda'); load('Summaries/N1/sumR5.Rda'); load('Summaries/N1/sumR6.Rda');
load('Summaries/N1/sumR7.Rda'); load('Summaries/N1/sumR8.Rda');


# alt model with normal prior on beta:
load('Summaries/N1/sumR1_2.Rda'); load('Summaries/N1/sumR2_2.Rda'); load('Summaries/N1/sumR3_2.Rda');
load('Summaries/N1/sumR4_2.Rda'); load('Summaries/N1/sumR5_2.Rda'); load('Summaries/N1/sumR6_2.Rda');
load('Summaries/N1/sumR7_2.Rda'); load('Summaries/N1/sumR8_2.Rda');
```

```{r, echo=FALSE}
# numbers (e.g. Beta1) refer to rows in the table

# Table 1:
Beta1= round(sumR1$statistics[1,1],2); Beta1_SD= round(sumR1$statistics[1,2],2);Beta1CI= round(c(sumR1$quantiles[1,1], sumR1$quantiles[1,5]) ,2); Beta1CI<- paste(Beta1CI[1], ", ", Beta1CI[2], sep="")
Beta1_2= round(sumR1_2$statistics[1,1],2); Beta1_2_SD= round(sumR1_2$statistics[1,2],2);Beta1_2CI= round(c(sumR1_2$quantiles[1,1], sumR1_2$quantiles[1,5]) ,2); Beta1_2CI<- paste(Beta1_2CI[1], ", ", Beta1_2CI[2], sep="")

Beta2= round(sumR2$statistics[1,1],2); Beta2_SD= round(sumR2$statistics[1,2],2);Beta2CI= round(c(sumR2$quantiles[1,1], sumR2$quantiles[1,5]) ,2); Beta2CI<- paste(Beta2CI[1], ", ", Beta2CI[2], sep="")
Beta2_2= round(sumR2_2$statistics[1,1],2); Beta2_2_SD= round(sumR2_2$statistics[1,2],2);Beta2_2CI= round(c(sumR2_2$quantiles[1,1], sumR2_2$quantiles[1,5]) ,2); Beta2_2CI<- paste(Beta2_2CI[1], ", ", Beta2_2CI[2], sep="")

Beta3= round(sumR3$statistics[1,1],2); Beta3_SD= round(sumR3$statistics[1,2],2);Beta3CI= round(c(sumR3$quantiles[1,1], sumR3$quantiles[1,5]) ,2); Beta3CI<- paste(Beta3CI[1], ", ", Beta3CI[2], sep="")
Beta3_2= round(sumR3_2$statistics[1,1],2); Beta3_2_SD= round(sumR3_2$statistics[1,2],2);Beta3_2CI= round(c(sumR3_2$quantiles[1,1], sumR3_2$quantiles[1,5]) ,2); Beta3_2CI<- paste(Beta3_2CI[1], ", ", Beta3_2CI[2], sep="")

Beta4= round(sumR4$statistics[1,1],2); Beta4_SD= round(sumR4$statistics[1,2],2);Beta4CI= round(c(sumR4$quantiles[1,1], sumR4$quantiles[1,5]) ,2); Beta4CI<- paste(Beta4CI[1], ", ", Beta4CI[2], sep="")
Beta4_2= round(sumR4_2$statistics[1,1],2); Beta4_2_SD= round(sumR4_2$statistics[1,2],2);Beta4_2CI= round(c(sumR4_2$quantiles[1,1], sumR4_2$quantiles[1,5]) ,2); Beta4_2CI<- paste(Beta4_2CI[1], ", ", Beta4_2CI[2], sep="")

Beta5= round(sumR5$statistics[1,1],2); Beta5_SD= round(sumR5$statistics[1,2],2);Beta5CI= round(c(sumR5$quantiles[1,1], sumR5$quantiles[1,5]) ,2); Beta5CI<- paste(Beta5CI[1], ", ", Beta5CI[2], sep="")
Beta5_2= round(sumR5_2$statistics[1,1],2); Beta5_2_SD= round(sumR5_2$statistics[1,2],2);Beta5_2CI= round(c(sumR5_2$quantiles[1,1], sumR5_2$quantiles[1,5]) ,2); Beta5_2CI<- paste(Beta5_2CI[1], ", ", Beta5_2CI[2], sep="")

Beta6= round(sumR6$statistics[1,1],2); Beta6_SD= round(sumR6$statistics[1,2],2);Beta6CI= round(c(sumR6$quantiles[1,1], sumR6$quantiles[1,5]) ,2); Beta6CI<- paste(Beta6CI[1], ", ", Beta6CI[2], sep="")
Beta6_2= round(sumR6_2$statistics[1,1],2); Beta6_2_SD= round(sumR6_2$statistics[1,2],2);Beta6_2CI= round(c(sumR6_2$quantiles[1,1], sumR6_2$quantiles[1,5]) ,2); Beta6_2CI<- paste(Beta6_2CI[1], ", ", Beta6_2CI[2], sep="")

Beta7= round(sumR7$statistics[1,1],2); Beta7_SD= round(sumR7$statistics[1,2],2);Beta7CI= round(c(sumR7$quantiles[1,1], sumR7$quantiles[1,5]) ,2); Beta7CI<- paste(Beta7CI[1], ", ", Beta7CI[2], sep="")
Beta7_2= round(sumR7_2$statistics[1,1],2); Beta7_2_SD= round(sumR7_2$statistics[1,2],2);Beta7_2CI= round(c(sumR7_2$quantiles[1,1], sumR7_2$quantiles[1,5]) ,2); Beta7_2CI<- paste(Beta7_2CI[1], ", ", Beta7_2CI[2], sep="")

Beta8= round(sumR8$statistics[1,1],2); Beta8_SD= round(sumR8$statistics[1,2],2);Beta8CI= round(c(sumR8$quantiles[1,1], sumR8$quantiles[1,5]) ,2); Beta8CI<- paste(Beta8CI[1], ", ", Beta8CI[2], sep="")
Beta8_2= round(sumR8_2$statistics[1,1],2); Beta8_2_SD= round(sumR8_2$statistics[1,2],2);Beta8_2CI= round(c(sumR8_2$quantiles[1,1], sumR8_2$quantiles[1,5]) ,2); Beta8_2CI<- paste(Beta8_2CI[1], ", ", Beta8_2CI[2], sep="")
```

Mean Difference of N+1 Preview Effects Between Alphabetical and Chinese Studies
--------------------------------------------------------------------------------
Measure                   | Prior on $\beta$     | Posterior $\beta$ (SD) [95% CrI]  
------------------------- |-----------------     |---------------------------------------------|
FFD                       |**Uniform(-200, 200)**|`r Beta1` (`r Beta1_SD`) [`r Beta1CI`]       |
FFD                       |Normal(0, $100^2$)    |`r Beta1_2` (`r Beta1_2_SD`) [`r Beta1_2CI`] |
SFD                       |**Uniform(-200, 200)**|`r Beta2` (`r Beta2_SD`) [`r Beta2CI`]       |
SFD                       |Normal(0, $100^2$)    |`r Beta2_2` (`r Beta2_2_SD`) [`r Beta2_2CI`] |
GD                        |**Uniform(-200, 200)**|`r Beta3` (`r Beta3_SD`) [`r Beta3CI`]       |
GD                        |Normal(0, $100^2$)    |`r Beta3_2` (`r Beta3_2_SD`) [`r Beta3_2CI`] |
FFD [unrelated word mask] |**Uniform(-200, 200)**|`r Beta4` (`r Beta4_SD`) [`r Beta4CI`]       |
FFD [unrelated word mask] |Normal(0, $100^2$)    |`r Beta4_2` (`r Beta4_2_SD`) [`r Beta4_2CI`] |
SFD [unrelated word mask] |**Uniform(-200, 200)**|`r Beta5` (`r Beta5_SD`) [`r Beta5CI`]       |
SFD [unrelated word mask] |Normal(0, $100^2$)    |`r Beta5_2` (`r Beta5_2_SD`) [`r Beta5_2CI`] |
GD [unrelated word mask]  |**Uniform(-200, 200)**|`r Beta6` (`r Beta6_SD`) [`r Beta6CI`]       |
GD [unrelated word mask]  |Normal(0, $100^2$)    |`r Beta6_2` (`r Beta6_2_SD`) [`r Beta6_2CI`] |
FFD [pseudo-word mask]    |**Uniform(-200, 200)**|`r Beta7` (`r Beta7_SD`) [`r Beta7CI`]       |
FFD [pseudo-word mask]    |Normal(0, $100^2$)    |`r Beta7_2` (`r Beta7_2_SD`) [`r Beta7_2CI`] |
GD [pseudo-word mask]     |**Uniform(-200, 200)**|`r Beta8` (`r Beta8_SD`) [`r Beta8CI`]       |
GD [pseudo-word mask]     |Normal(0, $100^2$)    |`r Beta8_2` (`r Beta8_2_SD`) [`r Beta8_2CI`] |

*Note*: The prior in bold is the one on which the results in the paper are based. 
