---
title: "Model sensitivity analysis [meta-regression]"
author: "Martin R. Vasilev"
date: "May 18, 2016"
output: html_document
---

```{r, echo=FALSE}
#Table 1:
load('Summaries/N1/sum40.Rda'); load('Summaries/N1/sum40_3.Rda');load('Summaries/N1/sum40_4.Rda')
load('Summaries/N1/sum40_5.Rda'); load('Summaries/N1/sum40_6.Rda'); load('Summaries/N1/sum40_7.Rda'); 

```

```{r, echo=FALSE}
# numbers (e.g. Mu1) refer to rows in the table

# Table 1:
Mu1= round(sum40$statistics[1,1],2); Mu1_SD= round(sum40$statistics[1,2],2);Mu1CI= round(c(sum40$quantiles[1,1], sum40$quantiles[1,5]) ,2); Mu1CI<- paste(Mu1CI[1], ", ", Mu1CI[2], sep="")
Tau1= round(sum40$statistics[2,1],2); Tau1_SD= round(sum40$statistics[2,2],2);Tau1CI= round(c(sum40$quantiles[2,1], sum40$quantiles[2,5]) ,2); Tau1CI<- paste(Tau1CI[1], ", ", Tau1CI[2], sep="")

Mu2= round(sum40_3$statistics[1,1],2); Mu2_SD= round(sum40_3$statistics[1,2],2);Mu2CI= round(c(sum40_3$quantiles[1,1], sum40_3$quantiles[1,5]) ,2); Mu2CI<- paste(Mu2CI[1], ", ", Mu2CI[2], sep="")
Tau2= round(sum40_3$statistics[2,1],2); Tau2_SD= round(sum40_3$statistics[2,2],2);Tau2CI= round(c(sum40_3$quantiles[2,1], sum40_3$quantiles[2,5]) ,2); Tau2CI<- paste(Tau2CI[1], ", ", Tau2CI[2], sep="")

Mu3= round(sum40_4$statistics[1,1],2); Mu3_SD= round(sum40_4$statistics[1,2],2);Mu3CI= round(c(sum40_4$quantiles[1,1], sum40_4$quantiles[1,5]) ,2); Mu3CI<- paste(Mu3CI[1], ", ", Mu3CI[2], sep="")
Tau3= round(sum40_4$statistics[2,1],2); Tau3_SD= round(sum40_4$statistics[2,2],2);Tau3CI= round(c(sum40_4$quantiles[2,1], sum40_4$quantiles[2,5]) ,2); Tau3CI<- paste(Tau3CI[1], ", ", Tau3CI[2], sep="")

Mu4= round(sum40_5$statistics[1,1],2); Mu4_SD= round(sum40_5$statistics[1,2],2);Mu4CI= round(c(sum40_5$quantiles[1,1], sum40_5$quantiles[1,5]) ,2); Mu4CI<- paste(Mu4CI[1], ", ", Mu4CI[2], sep="")
Tau4= round(sum40_5$statistics[2,1],2); Tau4_SD= round(sum40_5$statistics[2,2],2);Tau4CI= round(c(sum40_5$quantiles[2,1], sum40_5$quantiles[2,5]) ,2); Tau4CI<- paste(Tau4CI[1], ", ", Tau4CI[2], sep="")

Mu5= round(sum40_6$statistics[1,1],2); Mu5_SD= round(sum40_6$statistics[1,2],2);Mu5CI= round(c(sum40_6$quantiles[1,1], sum40_6$quantiles[1,5]) ,2); Mu5CI<- paste(Mu5CI[1], ", ", Mu5CI[2], sep="")
Tau5= round(sum40_6$statistics[2,1],2); Tau5_SD= round(sum40_6$statistics[2,2],2);Tau5CI= round(c(sum40_6$quantiles[2,1], sum40_6$quantiles[2,5]) ,2); Tau5CI<- paste(Tau5CI[1], ", ", Tau5CI[2], sep="")

Mu6= round(sum40_7$statistics[1,1],2); Mu6_SD= round(sum40_7$statistics[1,2],2);Mu6CI= round(c(sum40_7$quantiles[1,1], sum40_7$quantiles[1,5]) ,2); Mu6CI<- paste(Mu6CI[1], ", ", Mu6CI[2], sep="")
Tau6= round(sum40_7$statistics[2,1],2); Tau6_SD= round(sum40_7$statistics[2,2],2);Tau6CI= round(c(sum40_7$quantiles[2,1], sum40_7$quantiles[2,5]) ,2); Tau6CI<- paste(Tau6CI[1], ", ", Tau6CI[2], sep="")
```

Mean N+1 Preview Effect for All Languages [FFD]
-----------------------------------------------------------------------------------------------------------
Prior on $\theta$   | Prior on $\tau$   | Posterior $\theta$ (SD) [95% CrI]  |Posterior $\tau$ (SD) [95% CrI]    |
-----------------|-----------------  |---------------------------------|-----------------------------------|
**Uniform(-200, 200)**|**Uniform(0, 200)**|`r Mu1` (`r Mu1_SD`) [`r Mu1CI`] |`r Tau1` (`r Tau1_SD`) [`r Tau1CI`]|
Normal(0, $100^2$) |Uniform(0, 200)     |`r Mu2` (`r Mu2_SD`) [`r Mu2CI`] |`r Tau2` (`r Tau2_SD`) [`r Tau2CI`]|
Uniform(-200, 200)|Gamma(0.001, 0.001)|`r Mu3` (`r Mu3_SD`) [`r Mu3CI`] |`r Tau3` (`r Tau3_SD`) [`r Tau3CI`]|
Normal(0, $100^2$) |Gamma(0.001, 0.001)|`r Mu4` (`r Mu4_SD`) [`r Mu4CI`] |`r Tau4` (`r Tau4_SD`) [`r Tau4CI`]|
Uniform(-200, 200)|Normal(0, $100^2$) I(0,)|`r Mu5` (`r Mu5_SD`) [`r Mu5CI`] |`r Tau5` (`r Tau5_SD`) [`r Tau5CI`]|
Normal(0, $100^2$) |Normal(0, $100^2$) I(0,)|`r Mu6` (`r Mu6_SD`) [`r Mu6CI`] |`r Tau6` (`r Tau6_SD`) [`r Tau6CI`]|

*Note*: For Gamma distributions, the prior is on the precision (i.e. $1/\tau^2$). The priors in bold are the ones on which the results in the paper are based. 
